The Astropy Project

### 2017-11-10 main.tex
units section

\subsection{Units and quantities}\label{sec:units}
% Adrian, Marten

% TODO: should this just be called "Units"? all other sections in here look like
% they are named by the subpackage name -- quantity is an object within the
% package

The \texttt{astropy.units} subpackage adds support for representing units and
numbers with associated units (``quantities'') in code.
Historically, quantities in code have often been represented simply as numbers,
with units implied or noted via comments in the code because of considerations
about speed: having units associated with numbers inherently adds overhead to
numerical operations.
In \texttt{astropy.units}, \texttt{Quantity} objects subclass the \texttt{numpy}
array object and has been designed with speed in mind.
As of \astropypkg version 2.0, units and quantities are prevalent in most other
\astropypkg subpackages and are thus a key concept for using the package as a
whole.
Units are intimately entwined in the definition of astronomical coordinates and
thus nearly all functionality in the \texttt{astropy.coordinates} subpackage
(see \sectionname~\ref{sec:coordinates}) depends on this functionality.
For most other subpackages, quantities are at least accepted, and often expected
by default.

@@

\begin{description}
    \item[Speed improvements] \inlinecomment{TODO}{Marten}
    \item[Logarithmic units and magnitudes] By default, taking the logarithm of
        a \texttt{Quantity} object with non-dimensionless units intentionally
        fails.
        However, some well-known units are actually logarithmic quantities,
        where the logarithm of the value is taken with respect to some reference
        value.
        Examples include astronomical magnitudes, which are logarithmic fluxes,
        and decibels, which are more generic logarithmic ratios of quantities.
        Logarithmic, relative units are now supported in \texttt{astropy.units}.
    \item[Using quantities in tables] The \texttt{astropy.table} subpackage (see
        \sectionname~\ref{sec:table}) now supports using quantities in tables
        with the \texttt{QTable} class.
        As a result, units specified in FITS tables are supported, and tables
        with quantities can be read and written to various file formats.
    \item[Defining functions that require quantities] When writing code or
        functions that expect \texttt{Quantity} objects, we often want to
        enforce that the input units have the correct type.
        For example, we may want to require only length-type \texttt{Quantity}
        objects.
        These requirements often lead to implementing repetitive code for
        validating \texttt{Quantity} inputs.
        \texttt{astropy.units} now provides a \python decorator
        (\texttt{quantity\_input}) that does this verification automatically.
    \item[Interaction with \package{numpy} arrays] \inlinecomment{TODO}{Marten}
\end{description}

>>>>

\subsection{Units}\label{sec:units}
% Adrian

The \texttt{astropy.units} subpackage adds support for representing units and
numbers with associated units --- ``quantities'' --- in code.
Historically, quantities in code have often been represented simply as numbers,
with units implied or noted via comments in the code because of considerations
about speed: having units associated with numbers inherently adds overhead to
numerical operations.
In \texttt{astropy.units}, \texttt{Quantity} objects subclass the \texttt{numpy}
array object and has been designed with speed in mind.
As of \astropypkg version 2.0, units and quantities are prevalent in most other
\astropypkg subpackages and are thus a key concept for using the package as a
whole.
Units are intimately entwined in the definition of astronomical coordinates and
thus nearly all functionality in the \texttt{astropy.coordinates} subpackage
(see \sectionname~\ref{sec:coordinates}) depends on this functionality.
For most other subpackages, quantities are at least accepted, and often expected
by default.

@@

\begin{description}
    \item[Interaction with \package{numpy} arrays] The \texttt{Quantity} object
        is now a subclass of the \texttt{numpy.ndarray} object and therefore
        works well with many of the functions in \texttt{numpy} that support
        array operations. For example, \texttt{Quantity} objects with angular
        units can be passed in to the trigonometric functions implemented in
        \texttt{numpy} (e.g., \texttt{numpy.cos}) and do the right thing: the
        units are internally converted to radians (what the \texttt{numpy}
        trigonometric functions expect) before being passed to \texttt{numpy}.
    \item[Speed improvements] The \texttt{Quantity} object is now significantly
        faster than in early versions of \astropypkg. This is in large part due
        to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
        object, but even relative to more recent versions of \astropypkg,
        operations with \texttt{Quantity} objects are generally faster. This is
        largely thanks to improvements in the way \texttt{numpy} arrays can be
        subclassed.
    \item[Logarithmic units and magnitudes] By default, taking the logarithm of
        a \texttt{Quantity} object with non-dimensionless units intentionally
        fails.
        However, some well-known units are actually logarithmic quantities,
        where the logarithm of the value is taken with respect to some reference
        value.
        Examples include astronomical magnitudes, which are logarithmic fluxes,
        and decibels, which are more generic logarithmic ratios of quantities.
        Logarithmic, relative units are now supported in \texttt{astropy.units}.
    \item[Using quantities in tables] The \texttt{astropy.table} subpackage (see
        \sectionname~\ref{sec:table}) now supports using quantities in tables
        with the \texttt{QTable} class.
        As a result, units specified in FITS tables are supported, and tables
        with quantities can be read and written to various file formats.
    \item[Defining functions that require quantities] When writing code or
        functions that expect \texttt{Quantity} objects, we often want to
        enforce that the input units have the correct type.
        For example, we may want to require only length-type \texttt{Quantity}
        objects.
        These requirements often lead to implementing repetitive code for
        validating \texttt{Quantity} inputs.
        \texttt{astropy.units} now provides a \python decorator,
        \texttt{quantity\_input()}, that does this verification automatically.
\end{description}
